Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Finish proposal

After defining what data quality is and its characteristics, the next 
step would be data measurement or information quality in a project.

There are several research papers that try to find the answer, among which the 
work of \citet{lee2002aimq}. The authors tried to define an overall model along 
with an accompanying assessment instrument for quantifying information quality 
in an organization. The methodology has 3 main steps that need to be followed 
in order to apply it successfully:
  \begin{itemize}
    \item 2 $\times$ 2 model of what information quality means to managers;
    \item questionnaire for measuring information quality along the dimensions
    found in first step;
    \item two analysis techniques for interpreting the assessments captured 
    by the questionnaire.
  \end{itemize} 
After developing the technique, they applied it in 5 different organizations and
found that the tool proved to be practical.

@@

Having talked about data and ticket quality and its characteristics, we have 
another issue that inevitably arises in every software project: software waste. 
There are different researches that try to define what waste in software 
development is as well as its main types. One such paper is the one of 
\citet{sedano2017software}. The authors conducted a participant-observation 
study over a long period of time at Pivotal, a consultancy software development
company. They also interviewed multiple engineering and balanced theoretical 
sampling with analysis to elicit the following main types of waste in software
project:
  \begin{itemize}
    \item building the wrong feature or product;
    \item mismanaging backlog;
    \item extraneous cognitive load;
    \item rework;
    \item ineffective communication;
    \item waiting/multitasking;
    \item solutions too complex;
    \item psychological distress.
    \item \textbf{Relevance to our work}: this paper complements the previous 
      one on waste identification\cite{Korkala2014WasteIdentification}.
  \end{itemize}

@@

However, defining waste and its main types is not enough - one needs also
ways to identify such waste. \citet{Korkala2014WasteIdentification} propose a
technique to identify communication waste in agile software projects 
environments. The authors collaborated with a medium-sized American software 
company and conducted a series of observations, informal discussions, documents 
provided by the organization, as well as semi-structured interviews. Moreover,
the data collection for waste identification was split into 2 parts:
  \begin{itemize}
    \item \textbf{pre-development}: occurred before the actual implementation
      begun (e.g.\ backlog creation);
    \item \textbf{development}: happened throughout the implementation
      process (e.g.\ throughout sprints, retrospectives, sprint reviews,
      communication media).
  \end{itemize}
Eventually they reached two main conclusions:
  \begin{itemize}
    \item this proposed approach was efficient and the authors recommend it to
      companies if they'd like to conduct such processes internally;
    \item the research elicits 5 main categories for communication waste: lack
      of involvement, lack of shared understanding, outdated information, 
      restricted access to information, scattered information.
  \end{itemize}

@@

But what happens when a project gains maturity? A work that investigates the effects of process
maturity on quality, cycle time and effort is the one undergone by \citet{harter2000effects}. The
research proves and rejects several hypotheses, such as higher levels of process maturity lead 
to higher product quality, higher levels of process maturity are associated with increased cycle time,
higher product quality is associated with lower cycle time, higher levels of process maturity lead 
to increased development efforts in the project and higher product quality is associated with lower
development effort. The authors examined data coming from 30 projects belonging to the systems 
integration division from a large IT company and analyzed a couple of key variables and see how
they interact (i.e. process maturity, product quality, cycle time, development effort, product
size, domain/data/decision complexity and requirements ambiguity). They learned that the main
features they inspected are additively separable and linear. Moreover, they found out that 
higher levels of process maturity are associated with significantly higher quality, but also
with increased cycle times and development efforts. On the other hand, the reductions in cycle
time and effort resulting from improved quality outweigh the marginal increases from achieving
more process maturity.

@@

\subsection{Experimental Design}

We would like to begin the research by conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the list of projects
will be finalized once some tests will be run, and that is because
maybe some projects will have more valuable tickets for us to analyze and
we want to analyze multiple issue tracking systems 
(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
\citep{bugzilla}).

Then, as most issue tracking systems respond with JSON payloads through 
their REST APIs, we can easily extract components such as summary or 
description and analyze them. We have defined that the initial list of 
components that we want to inspect into three main categories:
  \begin{itemize}
    \item regular text - summary, description, story points, 
      text in comments, status (e.g. OPEN, WONTFIX, CLOSED);
    \item non-regular text (i.e. special structures) - stack traces,
      steps to reproduce;
    \item non-text - attachments in comments (e.g. images, screenshots
      when trying to show steps to reproduce).
  \end{itemize}

@@

Implementation wise, we would like to develop the application that will
perform both scraping, extraction and inspection in either Go or Java.

@@

\subsection{Variables Tested}

The independent variables proposed for testing are:
  \begin{itemize}
    \item presence and number of stack traces in a ticket;
    \item steps to reproduce (as described above - images or text);
    \item presence of screenshots in tickets;
    \item text components (e.g. summary, description) being either 
      succinct or detailed;
    \item grammar-free textual description;
    \item overall sentiment drawn from comments (e.g. angry or calm);
    \item complex or light discussion in comments.
  \end{itemize}

@@

>>>>

After defining what data quality is and its characteristics, the next 
step would be data measurement or information quality in a project. 
There are several research papers that try to find the answer, among which the 
work of \citet{lee2002aimq}. The authors tried to define an overall model along 
with an accompanying assessment instrument for quantifying information quality 
in an organization. The methodology has 3 main steps that need to be followed 
in order to apply it successfully:
  \begin{itemize}
    \item 2 $\times$ 2 model of what information quality means to managers;
    \item questionnaire for measuring information quality along the dimensions
    found in first step;
    \item two analysis techniques for interpreting the assessments captured 
    by the questionnaire.
  \end{itemize} 
After developing the technique, they applied it in 5 different organizations and
found that the tool proved to be practical.

@@

Having talked about data and ticket quality and its characteristics, we have 
another issue that inevitably arises in every software project: software waste. 
There are different researches that try to define what waste in software 
development is as well as its main types. One such paper is the one of 
\citet{sedano2017software}. The authors conducted a participant-observation 
study over a long period of time at Pivotal, a consultancy software development
company. They also interviewed multiple engineering and balanced theoretical 
sampling with analysis to elicit the following main types of waste in software
project:
  \begin{itemize}
    \item building the wrong feature or product;
    \item mismanaging backlog;
    \item extraneous cognitive load;
    \item rework;
    \item ineffective communication;
    \item waiting/multitasking;
    \item solutions too complex;
    \item psychological distress.
  \end{itemize}

@@

However, defining waste and its main types is not enough - one needs also
ways to identify such waste. \citet{Korkala2014WasteIdentification} propose a
technique to identify communication waste in agile software projects 
environments. The authors collaborated with a medium-sized American software 
company and conducted a series of observations, informal discussions, documents 
provided by the organization, as well as semi-structured interviews. Moreover,
the data collection for waste identification was split into 2 parts:
  \begin{itemize}
    \item \textbf{pre-development}: occurred before the actual implementation
      begun (e.g.\ backlog creation);
    \item \textbf{development}: happened throughout the implementation
      process (e.g.\ throughout sprints, retrospectives, sprint reviews,
      communication media).
  \end{itemize}
They reached two main conclusions:
  \begin{itemize}
    \item this proposed approach was efficient and the authors recommend it to
      companies if they'd like to conduct such processes internally;
    \item the research elicits 5 main categories for communication waste: lack
      of involvement, lack of shared understanding, outdated information, 
      restricted access to information, scattered information.
  \end{itemize}

@@

\citet{harter2000effects} explored the effects of process maturity on quality, cycle time and effort. The
research proves and rejects several hypotheses, such as higher levels of process maturity lead 
to higher product quality, higher levels of process maturity are associated with increased cycle time,
higher product quality is associated with lower cycle time, higher levels of process maturity lead 
to increased development efforts in the project and higher product quality is associated with lower
development effort. The authors examined data coming from 30 projects belonging to the systems 
integration division from a large IT company and analyzed a couple of key variables and see how
they interact (i.e. process maturity, product quality, cycle time, development effort, product
size, domain/data/decision complexity and requirements ambiguity). They learned that the main
features they inspected are additively separable and linear. Moreover, they found out that 
higher levels of process maturity are associated with significantly higher quality, but also
with increased cycle times and development efforts. On the other hand, the reductions in cycle
time and effort resulting from improved quality outweigh the marginal increases from achieving
more process maturity.

@@

Having reviewed the literature on state of the art approaches to what features
are most important when composing a high quality ticket, our work will
build on top of these methods and will try to improve the validity of the
results through statistical analysis. In the following subsections 
(\ref{experimental_design}, \ref{variables_tested} \ref{contributions}) we will
discuss how the experiment was designed, what variables were chosen
as dependent and independent as well as what contributions our study will bring.

\subsection{Experimental Design}\label{experimental_design}

The study we will undergo tries to identify the key components that make
for a valuable, high quality ticket. We would like to begin the research by 
conducting a statistical analysis 
over popular open source projects such as Mozilla or Apache and extract 
tickets most probably via REST APIs, however the list of projects
will be finalized once some tests will be run, and that is because
maybe some projects will have more valuable tickets for us to analyze and
we want to analyze multiple issue tracking systems 
(e.g. Apache uses Jira \citep{jira} while Mozilla uses Bugzilla 
\citep{bugzilla}).

Then, as most issue tracking systems respond with JSON payloads through 
their REST APIs, we can extract components such as summary or 
description and analyze them. We have defined that the initial list of 
components that we want to inspect into three main categories:
  \begin{itemize}
    \item regular text - summary, description, story points, 
      text in comments, status (e.g. OPEN, WONTFIX, CLOSED);
    \item non-regular text (i.e. special structures) - stack traces,
      steps to reproduce;
    \item non-text - attachments in comments (e.g. images, screenshots
      when trying to show steps to reproduce).
  \end{itemize}

@@

Implementation wise, we will develop the application that will
perform both scraping, extraction and inspection in either Go or Java.

@@

\subsection{Variables Tested}\label{variables_tested}

The independent variables proposed for testing are:
  \begin{itemize}
    \item presence and number of stack traces in a ticket;
    \item steps to reproduce (as described above - images or text);
    \item presence of screenshots in tickets and associated image quality metrics;
    \item text components (e.g. summary, description) being either 
      succinct or detailed;
    \item grammar-free textual description;
    \item overall sentiment drawn from comments (e.g. angry or calm);
    \item complex or light discussion in comments.
  \end{itemize}

@@

\subsection{Contributions}\label{contributions}

As we have previously mentioned, the main three contributions we will 
bring are as follows:
  \begin{itemize}
    \item explore the area of ticket quality through statistical analysis;
    \item inspect both tickets and other components of the software project
      (e.g. version control system) when analysing ticket quality;
    \item propose model for bug reports and/or feature requests.
  \end{itemize}
